Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-23 main.tex
fixing some simple things

\begin{proof}
  We proceed by induction on the number of inference steps in the
  proof of $C$ in $\FOMLS$. Consider the bottommost rule instance
  $\vlinf{\rr}{}{\Scons B}{\Scons A}$. By induction hypothesis we have
  a $\FOMLL$ proof $\Proof$ of $\sqn{\Scons A}$.
  We now make a case analysis on $\rr$:
  \begin{itemize}
    \setlength\itemsep{.5em}
    \item $\vlinf{\aiD}{}{\Scons{a\vlor\cneg a}}{\Scons\ttt}$ :
      In this case, we replace simultaneously in $\Pi$ the corresponding
      occurrences of $\ttt$ with $a \vlor \cneg a$ and the rule instance
      $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation
      $
        \vlderivation{
          \vlin{\vlor}{}{\sqn{a \vlor \cneg a}}{
            \vlin{\axr}{}{\sqn{a, \cneg a}}{
              \vlhy{}}}}
      $, and we get a proof $\Pi'$ of $\sqn{\Scons{a \vlor \cneg a}}$.
    %\item $\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$
     % In this case, we replace simultaneously in $\Pi$ the corresponding
     % occurrences of $\ttt$ with $\forall x.\ttt$ and the rule instance
     % $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation
     % $
     % \vlderivation{
     %   \vlin{\forall}{}{\sqn{\forall x.\ttt}}{
     %     \vlin{\axr}{}{\sqn{\ttt}}{
     %       \vlhy{}}}}
     % $, and we get a proof $\Pi'$ of $\sqn{\Scons{\forall x.\ttt}}$.
    \item In the other cases,
      by Lemma~\ref{lem:context}, we have a $\FOMLL$ proof of
      $\sqn{\cneg{\Scons A},\Scons B}$. We can compose them via $\cutr$:
      \begin{equation*}
        \vliinf{\cutr}{}{\sqn{\Scons B}}{\sqn{\Scons A}}{\sqn{\cneg{\Scons
          A},\Scons B}}
      \end{equation*}
      and then apply Theorem~\ref{thm:cutelim}.
  \end{itemize}
  \tocheck{}
  \end{proof}

>>>>

\begin{proof}
  We proceed by induction on the number of inference steps in the
  proof of $C$ in $\FOMLS$. Consider the bottommost rule instance
  $\vlinf{\rr}{}{\Scons B}{\Scons A}$. By induction hypothesis we have
  a $\FOMLL$ proof $\Proof$ of $\sqn{\Scons A}$. If $\rr$ is
  $\upsmash{\vlinf{\aiD}{}{\Scons{a\vlor\cneg a}}{\Scons\ttt}}$, we replace
  in $\Pi$ all corresponding occurrences of $\ttt$ with
  $a \vlor \cneg a$ and the rule instance
  $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation $ \vlderivation{
    \vlin{\vlor}{}{\sqn{a \vlor \cneg a}}{ \vlin{\axr}{}{\sqn{a, \cneg
          a}}{ \vlhy{}}}} $. This gives us a proof of
  $\sqn{\Scons{a \vlor \cneg a}}$. In all other cases, 
    %\item $\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$
     % In this case, we replace simultaneously in $\Pi$ the corresponding
     % occurrences of $\ttt$ with $\forall x.\ttt$ and the rule instance
     % $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation
     % $
     % \vlderivation{
     %   \vlin{\forall}{}{\sqn{\forall x.\ttt}}{
     %     \vlin{\axr}{}{\sqn{\ttt}}{
     %       \vlhy{}}}}
     % $, and we get a proof $\Pi'$ of $\sqn{\Scons{\forall x.\ttt}}$.
      by Lemmas~\ref{lem:shallow} and~\ref{lem:context}, we have a $\FOMLL$ proof of
      $\sqn{\cneg{\Scons A},\Scons B}$. We can compose them via $\cutr$:
      \begin{equation*}
        \vliinf{\cutr}{}{\sqn{\Scons B}}{\sqn{\Scons A}}{\sqn{\cneg{\Scons
          A},\Scons B}}
      \end{equation*}
      and then apply Theorem~\ref{thm:cutelim}.
  \end{proof}
